---
title: "graphic_description"
description: Here's an article which analyses a graphics about the size of 4 class of zooplankton.
author:
  - name: Avdia Alexandre
    url: {https://avdiaalexandre.github.io/avdiaalexandre_blog/}
categories : 
  - Data Sciences I
date: 11-15-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r}
SciViews::R
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
data <- read("zooplankton", package = "data.io")
```

## Data set description
This data set is about zooplankton.  Several datas have been measured, all linked to the morphology of zooplankton classes. Due to a matter of claruty, only 4 classes will be analysed.

```{r}
zooplankton <- read("zooplankton", package = "data.io", lang = "FR")

zooplankton_sub <- filter(zooplankton,
  class %in% c("Annélide", "Calanoïde", "Cyclopoïde", "Décapode"))

chart(data = zooplankton_sub, ~ size %fill=% class| class) +
  geom_histogram(bins = 25) +
  labs(y = "Effectifs", x = "Size (mm)") +
  scale_fill_viridis_d()
```

## Graphic analyse.
This graphic shows the distribution of the size in 4 zooplankton classes. We can see that Annelida is the class that can be the tallest, we can also notice that Calanoida have a big population around 1mm. The main conclusion is that those classes are mostly sized around and above 1mm. 
